Behavior Driven Development in Haskell

### 2012-10-20 paper.tex
Show full output for failing examples (as suggested by reviewer 1)

\begin{quote}
\small
\begin{verbatim}
$ runhaskell FibSpec.hs
fib
 - calculates arbitrary Fibonacci numbers FAILED [1]
\end{verbatim}
\end{quote}

@@

\begin{quote}
\small
\begin{verbatim}
$ runhaskell FibSpec.hs
fib
 - calculates arbitrary Fibonacci numbers
 - is efficient FAILED [1]
\end{verbatim}
\end{quote}

>>>>

\begin{quote}
\small
\begin{verbatim}
$ runhaskell FibSpec.hs

fib
 - calculates arbitrary Fibonacci numbers FAILED [1]

1) fib calculates arbitrary Fibonacci numbers FAILED
*** Falsifiable (after 1 test):
Small 1

Finished in 0.0021 seconds

1 example, 1 failure
\end{verbatim}
\end{quote}

@@

\begin{quote}
\small
\begin{verbatim}
$ runhaskell FibSpec.hs

fib
 - calculates arbitrary Fibonacci numbers
 - is efficient FAILED [1]

1) fib is efficient FAILED
expected: Just 2178309
 but got: Nothing

Finished in 0.0685 seconds

2 examples, 1 failure
\end{verbatim}
\end{quote}
